County Figures

### 2023-07-08 reports/county_figures.Rmd
add heatmap

      axis.text = element_text(              #axis text
                   size = 9),
      legend.text = element_text(size = 12),
      # t, r, b, l
      plot.margin = unit(c(1,.5,.5,.5), "cm"),
      legend.position = "right",
      strip.text.x = element_text(size = 11, face = "bold", color="white"),
      strip.text.y = element_text(size = 11, face = "bold", color="white",angle=270),
      strip.background = element_rect(fill = "#3E3D3D")
      ) %+replace%
      theme(...)

@@

  county <- county %>%
    left_join(versions) %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      TRUE ~ vlabel
    )) %>%
    mutate(vlabel =factor(vlabel,levels= c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
         "$P(S_1|untested)$ Centered at Survey Value",
         "$\\beta$ Centered at Survey Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values"))) %>%
    left_join(county_names) %>%
    mutate(name = ifelse(fips =="25007,25019", "Nantucket and Dukes", name)) %>%
    left_join(dates,  relationship = "many-to-many") %>%
    group_by(biweek) %>%
    mutate(mindate = min(date),
           maxdate = max(date)) %>%
    ungroup()

@@

correlations <- w_data %>%
  group_by(version) %>%
  summarize(Correlation = cor(exp_cases_median_std,mean_conc_std),
            vlabel =unique(vlabel)) %>%
  mutate(x=2.8,
         y=.1)

@@

```{r}
plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations with Wastewater Concentrations")

@@

covidestim_correlations <- w_data %>%
  filter(!is.na(infections_std)) %>%
  group_by(vlabel) %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(exp_cases_median_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=2.8,
         y=.1)

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "Correlations with Covidestim Infections")

@@

```{r,eval=save_figures}

@@

cor_waste %>%
  left_join(cor_covid) %>%
  mutate(vlabel = gsub(
    "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "Priors Do Not Vary by State and Date",
    vlabel, fixed=TRUE),vlabel=gsub(" at","\nat", vlabel)) %>%
  arrange(desc( `Correlation with Wastewater Concentrations`)) %>%
  rename(Implementation = vlabel) %>%
  kbl() %>%
  kable_styling(full_width = TRUE)

@@

@@

county %>% 
  mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .8,
             show.legend=FALSE,
             fill="#596281") +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

@@

county %>% 
    mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
  filter(biweek>=6) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill=vlabel),
             alpha = .5) +
  facet_wrap(~name,
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          legend.text=element_text(hjust=0)
          ) +
  scale_fill_manual(values = pal,
                    labels=TeX(unique(as.character(county$vlabel))))  +
  labs(x="",
       fill="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  guides(fill=guide_legend(nrow=2))

@@

>>>>

      axis.text = element_text(              #axis text
                   size = 9),
      legend.text = element_text(size = 12),
      # t, r, b, l
      plot.margin = unit(c(1,.5,.5,.5), "cm"),
      legend.position = "right",
      strip.text.x = element_text(size = 11, color="white"),
      strip.text.y = element_text(size = 11,  color="white",angle=270),
      strip.background = element_rect(fill = "#3E3D3D")
      ) %+replace%
      theme(...)

@@

  county <- county %>%
    left_join(versions) %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$\\overset{P(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}",
      version == "v3" ~ "$P(S_1|untested)$ Centered at Survey Value",
    )) %>%
    mutate(vlabel =factor(vlabel,levels= c(
        "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
         "$P(S_1|untested)$ Centered at Survey Value",
         "$\\beta$ Centered at Survey Value",
        "$\\overset{P(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}"))) %>%
    left_join(county_names) %>%
    mutate(name = ifelse(fips =="25007,25019", "Nantucket and Dukes", name)) %>%
    left_join(dates,  relationship = "many-to-many") %>%
    group_by(biweek) %>%
    mutate(mindate = min(date),
           maxdate = max(date)) %>%
    ungroup()

  wjoined <- wjoined %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$P(S_1|untested)$ Centered at Survey Value"
    ))

@@

correlations <- w_data %>%
  group_by(version) %>%
  summarize(Correlation = cor(exp_cases_median_std,mean_conc_std),
            vlabel =unique(vlabel)) %>%
  mutate(x=3.5,
         y=.1)

@@

```{r}
plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  theme(strip.text.x = element_text(size=12)) +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations with Wastewater Concentrations")

@@

covidestim_correlations <- w_data %>%
  filter(!is.na(infections_std)) %>%
  group_by(vlabel) %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(exp_cases_median_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=3.5,
         y=.1)

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  theme(strip.text.x = element_text(size=12)) +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "Correlations with Covidestim Infections")

plt_covidestim_pb

@@

```{r, fig.height=10, fig.width=14, eval=save_figures}

@@

cor_waste %>%
  left_join(cor_covid) %>%
  mutate(vlabel = gsub(
     "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
    "Priors Do Not Vary by State and Date",
    vlabel, fixed=TRUE),vlabel=gsub(" at","\nat", vlabel)) %>%
  arrange(desc( `Correlation with Wastewater Concentrations`)) %>%
  rename(Implementation = vlabel) %>%
  kbl() %>%
  kable_styling(full_width = TRUE)

@@

names(pal) <- c(#"$observed$", 
                '$P(S_1|untested)$ Centered at Survey Value',
                "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

county %>% 
  mutate(name=gsub("Nantucket and Dukes", "Nantucket\nand Dukes", name)) %>%
  mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .8,
             show.legend=FALSE,
             fill="#596281") +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  theme_c(strip.text.x=element_text(size=13,color='white')) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

## Fill by Version

@@

county_relab <- county %>%
  mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$P(S_1|untested)$ Centered at Survey Value",
    )) %>%
    mutate(vlabel =factor(vlabel,levels= c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
         "$P(S_1|untested)$ Centered at Survey Value",
         "$\\beta$ Centered at Survey Value",
       "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values"))) %>%
    mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
  filter(biweek>=6)

county_relab$vlabel %>% unique()

county_relab %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill=vlabel),
             alpha = .5) +
  facet_wrap(~name,
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          legend.text=element_text(hjust=0)
          ) +
  scale_fill_manual(values = pal,
                    labels=TeX(unique(as.character(county_relab$vlabel))))  +
  labs(x="",
       fill="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  guides(fill=guide_legend(nrow=2))

@@

# Heatmap

######################################################
# HEATMAP OF RATIO OF ESTIMATED TO OBSERVED
######################################################

heatmap_dat <- county %>%
  filter(version == "v7") %>%
  group_by(biweek, name, exp_cases_median, positive) %>%
  summarize(date = min(date)) %>%
  ungroup()

wide <- heatmap_dat %>%
    mutate(ratio= exp_cases_median/positive) %>%
  select(-c(exp_cases_median, positive)) %>%
  pivot_wider(names_from=name,values_from =ratio)

heatmap_dat %>%
  # mutate(county_name = gsub("Nantucket", "Nantucket and", name)) %>%
  mutate(ratio=exp_cases_median/positive) %>%
  mutate(date_lab = format(as.POSIXct(date),format="%b %d %Y")) %>%
  group_by(name) %>%
  mutate(m = median(ratio)) %>%
  ungroup() %>%
  ggplot(aes(x=fct_reorder(date_lab, date),
             y = fct_reorder(name,m),
             fill =exp_cases_median/positive)) +
  geom_tile() +
 # scale_x_discrete(breaks=breaks_date, labels = breaks_date)  +
  viridis::scale_fill_viridis(option="rocket", direction=-1) +
  labs(x="",
       y= "",
       fill = "Ratio of Estimated Infections\nto Observed Infections",
       title = "Ratio of Median Estimated Infections to Observed Infections\nfor Counties in Massachusetts") +
  theme_c() +
  theme(axis.text.x = element_text(size=11, angle=90),
        axis.text.y = element_text(size = 17),
        axis.title = element_text(size=16),
        legend.title = element_text(face="bold", size=18),
        plot.title =element_text(size=22),
        plot.subtitle = element_text(size=20))

# which biweeks are highest?
heatmap_dat %>%
  mutate(ratio=exp_cases_median/positive) %>%
  group_by(biweek) %>%
  summarize(m=median(ratio),
            date=min(date)) %>%
  arrange(desc(m))

ggsave(here('figures/ma_county_heatmap.pdf'),
       height=10,
       width =13,
       dpi=400)
